---
title: "fifth_post"
description: |
 Blog Post 5
author:
  - name: Sathvik Thogaru 
    url: https://thogarusathvik.github.io/Text-as-Data-Project/
    
date: 04-18-2022
output:
  distill::distill_article:
    self_contained: false
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

<style>
body {
text-align: justify}
</style>

## intro

loading required libraries 

All the twitter data in the JSON format. It is later converted to csv format and stored in the combined_data.csv file which is loaded here

```{r}
library(quanteda)
library(tidyr)
library(quanteda.textplots)
library(dplyr)
library(readr)
library(stopwords)
library(ggplot2)
library(tidytext)
library(quanteda.sentiment)
library(plotrix)
library(radarchart)
#load("../../data/fifth_post.RData")



df <- read_csv("../../data/combined_data.csv") %>% select(-1)
```

Now we just wnt to know where more tweets are from?

```{r}

df %>% filter(!is.na(user_location)) %>% 
  count(user_location, sort = TRUE) %>%
  mutate(user_location = reorder(user_location, n)) %>%
  top_n(10) %>%
  ggplot(aes(x = user_location, y = n, na.rm = TRUE, fill = n)) +
  geom_col() +
  coord_flip() +
      labs(x = "Location",
      y = "Count",
      title = "Where more tweets are from - unique locations ") +  theme_classic()+
  theme(legend.position="none")
```
Looks like most of the tweets are from India, followed by the USA sates and England countries.

## tokenization and dfm

stop words are removed using the collection " stopwords-iso". the stopwords-iso has 1298 unique stopwords in english language

```{r}
tweets <- df$text
stop_words <- stopwords(source = "stopwords-iso")
tweets <- tweets %>% tokens %>% 
  tokens_remove(pattern = phrase(stop_words), valuetype = 'fixed')

dfm_tokens <- dfm(tweets)
topfeatures(dfm_tokens, 20)
```

wordcloud of all the tokens

```{r}
word_counts <- as.data.frame(sort(colSums(dfm_tokens),dec=T))
colnames(word_counts) <- c("count")
word_counts$word <- row.names(word_counts)
textplot_wordcloud(dfm_tokens)

```

Lokks like the discussions were around omicron, vaccines, pandemic, healthcare and deaths caused by coronavirus virus


## save RData

```{r}
# save.image(file = "fifth_post.RData")
```


## fcm

```{r}
text_dfm <- dfm_trim(dfm_tokens, min_termfreq = 500)

# create fcm from dfm
text_fcm <- fcm(text_dfm)

# check the dimensions (i.e., the number of rows and the number of columnns)
# of the matrix we created
dim(text_fcm)
```


```{r}
# pull the top features
myFeatures <- names(topfeatures(text_fcm, 50))

# retain only those top features as part of our matrix
top_text_fcm <- fcm_select(text_fcm, pattern = myFeatures, selection = "keep")

# check dimensions
dim(top_text_fcm)
```


```{r}
# compute size weight for vertices in network
size <- log(colSums(top_text_fcm))

# create plot
textplot_network(top_text_fcm, vertex_size = size / max(size) * 3)
```

## sentiment analysis bing and nrc

```{r}
tweets_bing<-word_counts%>% 
  # Implement sentiment analysis using the "bing" lexicon
  inner_join(get_sentiments("bing")) 

perc<-tweets_bing %>% 
  count(sentiment)%>% #count sentiment
  mutate(total=sum(n)) %>% #get sum
  group_by(sentiment) %>% #group by sentiment
  mutate(percent=round(n/total,2)*100) %>% #get the proportion
  ungroup()

label <-c( paste(perc$percent[1],'%',' - ',perc$sentiment[1],sep=''),#create label
     paste(perc$percent[2],'%',' - ',perc$sentiment[2],sep=''))

pie3D(perc$percent,labels=label,labelcex=1.1,explode= 0.1, 
      main="Worldwide Sentiment")
```

People showed more negative sentiments during the third wave in January and February months 


```{r}
word_counts %>%
  # implement sentiment analysis using the "nrc" lexicon
  inner_join(get_sentiments("nrc")) %>%
  # remove "positive/negative" sentiments
  filter(!sentiment %in% c("positive", "negative")) %>%
  #get the frequencies of sentiments
  count(sentiment,sort = T) %>% 
  #calculate the proportion
  mutate(percent=100*n/sum(n)) %>%
  select(sentiment, percent) %>%
  #plot the result
  chartJSRadar(showToolTipLabel = TRUE, main = "NRC Radar")
```

People display anger, disgust, fear, and sadness toward the pandemic and related death and there is less joy 
and anticipation.
